\chapter{Executive Board Elections}\label{Bylaw:ExecutiveBoardElections}

\section{Schedule}\label{chap:ExecutiveBoardElectionsSchedule}
    The election of the executive board, hereafter referred to as the \gls{Election}, shall be held at least once a year and shall take place no later than the second to last full week of C term. 

\section{Nominations}\label{chap:ExecutiveBoardElectionsNominations}
    The \gls{ExecutiveBoard} shall notify all \glspl{ActiveMember} of the \gls{Election} one week prior to the \gls{Election}. Any \gls{ActiveMember} may nominate any undergraduate \gls{ActiveMember}. Nominations shall be submitted to the \gls{ExecutiveBoard} no later than 24 hours prior to the executive election. Upon receiving a nomination, the \gls{ExecutiveBoard} will immediately notify the nominee. To be a candidate in the \gls{Election}, the nominee must accept the nomination prior to the start of the \gls{Election}. The nomination is assumed to be automatically accepted in the case of a self nomination. 

\section{Moderator}\label{chap:ExecutiveBoardElectionsModerator}
    The election for each \gls{Executive} position shall be moderated by the highest ranking \gls{Executive} who is not a candidate for the position.

\section{Procedure}\label{chap:ExecutiveBoardElectionsProcedure}
    When electing an \gls{Executive} the following procedure will be followed:
    \begin{enumerate}
        \item{The names of all candidates for the position shall be read.}
        \item{All candidates shall be asked to leave the room.}
        \item{Candidates shall be selected one by one, in last name alphabetical order. Each selected candidate shall return to the room and may deliver a speech no longer than five minutes. The general body may then ask the selected candidate questions for up to five minutes, following which the selected candidate shall be asked to leave the room.}
        \item{Following this, the general body may discuss the candidates for up to 15 minutes.}
        \item{All candidates shall return to the room and balloting to elect an \gls{Executive} shall occur as described in \Gls{Bylaw} \ref{Bylaw:Voting:Electing}}
    \end{enumerate}

\section{Transition}\label{chap:ExecutiveBoardElectionsTransistions}
    The newly elected \gls{ExecutiveBoard} shall take office immediately following D term. Throughout D term, the newly elected \gls{ExecutiveBoard} shall be mentored by the current \gls{ExecutiveBoard}. This shall include, at minimum, the following:
    \begin{enumerate}
        \item{The newly elected \gls{ExecutiveBoard} shall attend all \glspl{ExecutiveBoardMeeting}.}
        \item{The newly elected \gls{ExecutiveBoard} shall attend all \glspl{GeneralBodyMeeting}.}
        \item{The newly elected \gls{ExecutiveBoard} shall participate in the \gls{Appointment} of \glspl{Officer}.}
        \item{Each newly elected \gls{Executive} shall meet with their position's current \gls{Executive}.}
        \item{Each newly elected \gls{Executive} shall maintain active member status.}
    \end{enumerate}