\chapter{Meetings}\label{Bylaw:Meetings}

\section{Classes of Meetings}\label{Bylaw:Meetings:Classes}
	The \gls{Branch} shall have three classes of meetings:
	\begin{itemize}
		\item{\textbf{\Gls{GeneralBodyMeeting}}: \Glsdesc{GeneralBodyMeeting}. During \glspl{GeneralBodyMeeting} all administrative business shall be handled, including but not limited to officer reports, elections, and motions.}
		\item{\textbf{\Gls{TermlyMeeting}}: \Glsdesc{TermlyMeeting}.}
		\item{\textbf{\Gls{ExecutiveBoardMeeting}}: \Glsdesc{ExecutiveBoardMeeting}. During \glspl{ExecutiveBoardMeeting}, all sensitive business shall be handled.}
	\end{itemize}

\section{Meeting Attendance}\label{Bylaw:Meetings:Attendance}
	There shall be four classes of meeting attendance for all \gls{Branch} meetings.
	\begin{itemize}
		\item{\textbf{In Attendance}: The person was present for the majority of the meeting.}
		\item{\textbf{Excused}: The person was not present for the majority of the meeting and they sent a valid excuse to the \gls{ExecutiveBoard} prior to the start of the meeting.}
		\item{\textbf{Absent}: The person was not present for the majority of the meeting and they did not send a valid excuse to the \gls{ExecutiveBoard} prior to the start of the meeting.}
		\item{\textbf{On Leave}: The person was away from campus for the \gls{AcademicTerm} in which the meeting was held for reasons including but not limited to \gls{IQP}, \gls{MQP}, or Co-op.}
	\end{itemize}

\section{Formal Motions}\label{Bylaw:Meetings:Motions}
	During a \gls{GeneralBodyMeeting}, and \gls{ActiveMember} may make a formal motion. The motion shall be discussed and, if necessary, voted on as outlined in \Gls{Bylaw} \ref{Bylaw:Voting:Motion}. Motions include, but are not limited to, the following: 
	\begin{itemize}
		\item{Amending the \gls{Branch} \Glspl{Bylaw}.}
		\item{Approving purchases with \gls{Branch} funds.}
		\item{Impeaching an \gls{Officer}.}
	\end{itemize}

