\documentclass[12pt]{report}
\usepackage[margin=1.5in]{geometry}
\usepackage{MnSymbol,wasysym}

\pagenumbering{gobble}

\begin{document}
\section*{IEEE WPI Student Branch}
\subsection*{Lounge Policy}
By gaining access to WPI's IEEE Lounge in AK 106, you agree to abide by the following rules. Having our own space on campus is a privilege, and these rules help keep the space functional and clean for everyone! The executive board reserves the right to revoke lounge access if these policies are not respected.

\begin{enumerate}
    \item{Regular access to the lounge is reserved exclusively for lounge members. The requirements for lounge members are defined in the bylaws.}
    \item{Guests are permitted for short periods of time under supervision by a lounge member.}
    \item{Do not host meetings in the lounge unless they are IEEE-related.}
    \item{Do not take other people's belongings. This includes, but is not limited to, food, electronics, and personal items.}
    \item{Do not remove shared items from the lounge. This includes, but is not limited to, supplies, furniture, and equipment.}
    \item{Clean up after you leave. This includes, but is not limited to, ensuring surfaces and project areas are kept tidy.}
    \item{Please try and label food in the fridge with your name.  Food over a week old will be thrown out without notice.}
    \item{Be nice to others! We're all friends here! \Large\smiley{}}
\end{enumerate}

\noindent We're trying to build an open, fun, collaborative place on campus. This space belongs to all of us — we want you to bring your personal touch and help make it better! There aren't any rules on what items should/shouldn't be in the lounge, so feel free to bring whatever you want. If there's something you think the club should purchase or restock, please let the executive board know!

\vspace{\fill}
\noindent \normalsize{Revised \today}
\hspace{\fill}
github.com/ieee-wpi/policies
\end{document}